\documentclass[phd]{ucbthesis}

\usepackage{algorithm,algpseudocode}

\usepackage[
  backend=biber,
  citestyle=authoryear,
  url=false
]{biblatex}

\usepackage{epigraph}
\usepackage[utf8]{inputenc}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{thesis} % common preamble for main document and standalone figures

\usepackage[mode=buildnew]{standalone}  % compile figures separately (fast, good for editing)
%\usepackage[mode=tex]{standalone}       % compile figures inline (slow, use only for final version)

\usepackage[capitalize]{cleveref} % should be included last

% biblatex config
\addbibresource{refs.bib}
\renewcommand\bibinitdelim{\addnbthinspace}

\captionsetup{subrefformat=parens}

\setsecnumdepth{subsection}
\settocdepth{subsection}

\begin{document}

\title{Nature of the spin glass phase in models with long-range interactions}
\author{Matthew Wittmann}
\degreesemester{Fall}
\degreeyear{2015}
\degree{Doctor of Philosophy}
\chair{Dr. A. Peter Young}
\othermembers{%
  Dr. B. Sriram Shastry \\
  Dr. Joshua Deutsch
}
\numberofmembers{3}
\field{Physics}
\campus{Santa Cruz}

\maketitle
\approvalpage
\copyrightpage

\begin{frontmatter}
\DoubleSpacing
\include{abstract}
\clearpage
\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables
\clearpage

\begin{dedication}
\begin{center}
  To my parents,
  for their endless love and support.
\end{center}
\end{dedication}

\begin{acknowledgements}
  First and foremost I would like to thank my advisor, Peter Young, for his
  patience, support, and for his dedication to presenting and explaining ideas
  clearly in teaching and writing, which has been an inspiration to me. I would
  also like to thank him for the many opportunities he has provided me to
  enrich my education, including summer courses in Germany and France and a
  stay at the Max Planck Institute in Dresden. Additionally I would like to
  thank the remaining members of the reading committee, Sriram Shastry and Josh
  Deutsch, for their guidance and useful discussions both inside and outside
  the classroom.

  I have benfitted immensely from the mentorship of Itay Hen, who taught me
  much of what I know about the topics of quantum Monte Carlo and quantum
  adiabatic algorithms, and has advised me on several research projects in the
  latter, all while juggling his own responsibilities as a postdoc and rising
  researcher in the field.

  I have had the opportunity to collaborate with several excellent researchers;
  I would like to thank Helmut Katzgraber, Jonathan Machta, and Burcu Yucesoy
  for many useful discussions and for their contributions to the work which is
  reprinted in \cref{chap:overlap}. Helmut deserves special thanks for donating
  a large chunk of his computer time for the simulations.

  A big thanks goes out to my fellow graduate students and friends in the
  department who have made my time in Santa Cruz enjoyable and unforgettable. A
  special thanks goes to the musicians, backpackers, and cyclists with whom I
  have shared many adventures.

  Finally, I would like to thank my best friend and partner Tia Plautz for her
  moral support and encouragement during the preparation of this thesis, and
  all of the unforgettable memories made during our time in Santa Cruz and
  abroad. I'm looking forward to seeing the world together!

  The text of this dissertation includes reprints of the following material,
  previously published or submitted for publication:
  \begin{itemize}
    \item\fullcite{wittmann2012spin}
    \item\fullcite{wittmann2014finite}
    \item\fullcite{wittmann2015connection}
  \end{itemize}
  The co-author listed in these publications directed and supervised the
  research which forms the basis for the dissertation. The text of this
  dissertation also includes excerpts from the following collaboration,
  \begin{itemize}
    \item\fullcite{wittmann2014low},
  \end{itemize}
  where I contributed simulation data for the one-dimensional long-range
  models, analysis of the data for all models, and wrote some of the text.
\end{acknowledgements}
\end{frontmatter}

\pagestyle{headings}

\DoubleSpacing

\include{chap-intro}
\include{chap-numerical}
\include{chap-nonextensive}
\include{chap-overlap}
\include{chap-connection}
\include{chap-fss}

%\appendix
%\include{app-wolff}

\SingleSpacing

\printbibliography

\end{document}
